### 2025-04-22 paper/abs_en.tex
feat: paper polish2

In the process of modern agriculture’s transformation towards intelligence, precision harvesting has become a key factor in improving agricultural production efficiency and quality. Among these, the weighing of fruits and vegetables during harvest is an essential part of precision harvesting. With the widespread application of electronic scales, their role in fruit and vegetable harvesting on smart farms has become increasingly prominent. However, at present, fruit and vegetable harvesting still largely depends on manual operations, making the accurate recording of harvested fruits’ weights and the scientific management of fruit yields particularly urgent.

Against this backdrop, this research conducts an in-depth survey of agricultural production activities, applying software engineering principles to identify and analyze specific requirements. It utilizes various software technologies, including web development techniques and YOLO-based fruit and vegetable recognition technologies, to design and develop a cloud-based agricultural fruit weighing software. This software achieves stable and high-performance data processing capabilities, provides efficient and rich information management functions, and offers multi-dimensional data visualization. Finally, the software’s various functionalities were tested, and performance tests on key interfaces were conducted in specific hardware environments, demonstrating the core indicators of the software to meet the deployment needs in practical production environments.

>>>>

In the process of modern agriculture's transformation towards intelligence, precision harvesting has become a key factor in improving agricultural production efficiency and quality. Among these, the weighing of fruits and vegetables during harvest is an essential part of precision harvesting. With the widespread application of electronic scales, their role in fruit and vegetable harvesting on smart farms has become increasingly prominent. However, at present, fruit and vegetable harvesting still largely depends on manual operations, making the accurate recording of harvested fruits' weights and the scientific management of fruit yields particularly urgent.

Against this backdrop, this research conducts an in-depth survey of agricultural production activities, applying software engineering principles to identify and analyze specific requirements. It utilizes various software technologies, including web development techniques and YOLO-based fruit and vegetable recognition technologies, to design and develop a cloud-based agricultural fruit weighing software. This software achieves stable and high-performance data processing capabilities, provides efficient and rich information management functions, and offers multi-dimensional data visualization. Finally, the software's various functionalities were tested, and performance tests on key functionalities were conducted in specific hardware environments, demonstrating the core indicators of the software to meet the deployment needs in practical production environments.

### 2025-04-22 paper/c3.tex
feat: paper polish2

Spring 框架中的核心模块提供了 IOC (控制反转)和 DI (依赖注入)这两大功能；切面模块提供了 AOP (面向切面编程)支持；数据访问/集成模块主要提供了对象关系映射、事务、数据库连接、Java 消息服务以及对象 XML 映射这五个功能；Web 服务模块为应用提供了编解码、过滤器、跨域、WebFlux(响应式 Web 编程)、WebMVC(模型-视图-控制器模式)等功能；工具模块则为应用提供了服务监控、日志记录等扩展功能；消息模块提供了丰富易用的消息队列集成；测试模块则为应用提供了强大的单元测试支持\cite{Spring-框架概述}。

@@

4、后处理：在预测完成后，YOLOv8 通常采用一些后处理方法，如非极大值抑制（Non-Maximum Suppression，NMS）或软非极大值抑制（Soft-NMS）\cite{SuperYOLO8}，来去除重复的检测结果，提高检测的准确性。

@@

MQTT（Message Queuing Telemetry Transport）即消息队列遥测传输协议，是一种轻量级的发布/订阅模式的消息传输协议。本软件采用 MQTT 作为称重消息的发布/订阅的通信协议。在软件中，发送 MQTT 消息上传称重信息具有以下优势：

（1）低带宽和低功耗：MQTT 协议非常适合在低带宽和低功耗的环境下使用。对于电子秤等物联网设备来说，通常需要在有限的网络资源和电池电量下进行数据传输。MQTT 协议通过采用轻量级的消息格式和高效的发布/订阅模式，可以大大降低网络带宽的占用和设备的功耗。例如，在一些偏远地区或者移动环境下，网络带宽可能非常有限，此时使用 MQTT 协议可以确保电子秤能够及时上传称重信息，同时不会对网络造成过大的负担\cite{Jia2015}。

（2）实时性和可靠性：MQTT 协议支持通过 QoS（Quality of Service，服务质量）来控制传输质量。可以根据不同的应用需求，选择不同的消息传输质量级别。在 MQTT 协议中，QoS 有三种级别\cite{Jia2015}，分别是：

@@

（3）易于扩展和集成：MQTT 协议具有良好的扩展性和集成性。可以很容易地与其他物联网协议和技术进行集成，如 CoAP、HTTP、WebSocket 等。同时，MQTT 协议的发布/订阅模式可以支持大规模的设备连接和数据传输，适用于构建物联网应用平台。例如，在智慧农业大棚测控系统中，采用 MQTT 协议将智慧大棚测控系统和阿里云物联网平台结合在一起，通过手机 APP 或 PC 软件访问阿里云服务器数据库，实现了移动终端对农业大棚实时监测和控制\cite{Liang2020}。

>>>>

Spring 框架中的核心模块提供了 IOC(控制反转)和 DI (依赖注入)这两大功能；切面模块提供了 AOP (面向切面编程)支持；数据访问/集成模块主要提供了对象关系映射、事务、数据库连接、Java 消息服务以及对象 XML 映射这五个功能；Web 服务模块为应用提供了编解码、过滤器、跨域、WebFlux(响应式 Web 编程)、WebMVC(模型-视图-控制器模式)等功能；工具模块则为应用提供了服务监控、日志记录等扩展功能；消息模块提供了丰富易用的消息队列集成；测试模块则为应用提供了强大的单元测试支持\cite{Spring-框架概述}。

@@

4、后处理：在预测完成后，YOLOv8 通常采用一些后处理方法，如非极大值抑制(Non-Maximum Suppression，NMS)或软非极大值抑制(Soft-NMS)\cite{SuperYOLO8}，来去除重复的检测结果，提高检测的准确性。

@@

MQTT(Message Queuing Telemetry Transport)即消息队列遥测传输协议，是一种轻量级的发布/订阅模式的消息传输协议。本软件采用 MQTT 作为称重消息的发布/订阅的通信协议。在软件中，发送 MQTT 消息上传称重信息具有以下优势：

(1)低带宽和低功耗：MQTT 协议非常适合在低带宽和低功耗的环境下使用。对于电子秤等物联网设备来说，通常需要在有限的网络资源和电池电量下进行数据传输。MQTT 协议通过采用轻量级的消息格式和高效的发布/订阅模式，可以大大降低网络带宽的占用和设备的功耗。例如，在一些偏远地区或者移动环境下，网络带宽可能非常有限，此时使用 MQTT 协议可以确保电子秤能够及时上传称重信息，同时不会对网络造成过大的负担\cite{Jia2015}。

(2)实时性和可靠性：MQTT 协议支持通过 QoS(Quality of Service，服务质量)来控制传输质量。可以根据不同的应用需求，选择不同的消息传输质量级别。在 MQTT 协议中，QoS 有三种级别\cite{Jia2015}，分别是：

@@

(3)易于扩展和集成：MQTT 协议具有良好的扩展性和集成性。可以很容易地与其他物联网协议和技术进行集成，如 CoAP、HTTP、WebSocket 等。同时，MQTT 协议的发布/订阅模式可以支持大规模的设备连接和数据传输，适用于构建物联网应用平台。例如，在智慧农业大棚测控系统中，采用 MQTT 协议将智慧大棚测控系统和阿里云物联网平台结合在一起，通过手机 APP 或 PC 软件访问阿里云服务器数据库，实现了移动终端对农业大棚实时监测和控制\cite{Liang2020}。
